Validating RDF Data Quality using Constraints to Direct the Development of Constraint Languages

### 2015-09-14 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
feedback Kai findings

SBE sciences require high-quality data for their empirical research. For more than a decade, members of the SBE community have been developing and using a
metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)}, \footnote{\url{http://www.ddialliance.org/Specification/}}
an XML format to disseminate, manage,
and reuse data collected and archived for research \cite{Vardigan2008}. 
In XML, the definition of schemas containing constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
With the rise of the Web of Data, data professionals and institutions are very interested in publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate discovery and reuse. Therefore, not only established vocabularies like SKOS are used; 
recently, members of the SBE and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.

@@

Note that there is a correlation between the severity of a constraint and the classification according to the expressivity of constraint languages of its type: \emph{RDFS/OWL Based} constraints are in many cases classified with an \emph{error} level as they typically represent basic and important constraints; there is a reason why they have been included in the vocabulary specification. Although we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
% Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
% For some use cases, 
% validating \emph{vocabulary constraints} may be more important than validating \emph{simple} or \emph{complex constraints}.
% For other use cases,
% validating \emph{error constraints} may be sufficient without taking \emph{warning} and \emph{informational constraints} into account.
% We evaluated the (meta)data quality of large real world data sets represented by multiple and different vocabularies to get an understanding  
% (1) which sets of constraint types (on different levels of complexity) and 
% (2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).

@@

85\% of the QB constraints are \emph{error} constraints.
More than 50\% of the DDI-RDF and SKOS constraints, however, are \emph{informational} constraints.
1/6 of the DDI-RDF violations are caused by \emph{error} constraints and
almost all QB violations and 59\% of the SKOS violations are caused by \emph{warning} constraints.  
%Constraints are serious when they violate the integrity of vocabularies.
%For well-established vocabularies, it is well documented and the experience is high how to guarantee this integrity
%which is not the case or newly-developed vocabularies.
\begin{hyp}
%\ke{das ist doch das gleiche wie 4, oder?}\bz{Stimme Kai zu. Finding 4 und 6 koennte man zusammenfassen oder falls es doch Unterschiede gibt, muessen die staerker hervorgehoben werden.}
For well-established vocabularies, data quality is high as serious violations rarely appear. For newly developed vocabularies, however, data quality is worse as serious violations occur partially.   
\end{hyp}

@@

The fact that regardless of the language 1/2 of all constraints are \emph{informational} indicates that the purpose of constraints for users is mostly just to point to desirable but not necessary data improvements in terms of syntax and semantics of vocabularies.

\begin{hyp}
Regardless of the type of the used language, there are only a few violations raised by important constraints which stands for good data quality in general.
In contrast, constraints of low severity, expressed by RDFS/OWL or high-level constraint languages, are violated to a large extent (80\%), whereas more serious constraints, expressed by SPARQL, are violated to an even larger extend (94\%).
%Violations caused by constraints expressed by RDFS/OWL or high-level constraint languages are of low severity (as the important constraints are satisfied), whereas the violation of constraints formulated by SPARQL is more serious. There is a significant demand for languages that support the expression of SPARQL Based constraints.
\end{hyp}

The reason why there is a significant demand for languages supporting \emph{SPARQL Based} constraints is that 94\% of all violations, which are caused by \emph{SPARQL Based} constraints, are also raised by \emph{warning} constraints. This means that data quality may be improved in case these \emph{warning} constraints are adequately tackled which is more likely when these constraints are expressible not only by SPARQL but also by high-level constraint languages enabling to formulate constraints more intuitively and concisely.

>>>>

SBE sciences require high-quality data for their empirical research. For more than a decade, members of the SBE community have been developing and using a
metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)}, \footnote{\url{http://www.ddialliance.org/Specification/}}
an XML format to disseminate, manage,
and reuse data collected and archived for research. 
%\cite{Vardigan-2008}. 
In XML, the definition of schemas containing constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
With the rise of the Web of Data, data professionals and institutions are very interested in publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate discovery and reuse. Therefore, not only established vocabularies like SKOS are used; 
recently, members of the SBE and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.

@@

Note that there is a correlation between the severity of a constraint and the classification according to the expressivity of constraint languages of its type: \emph{RDFS/OWL Based} constraints are in many cases classified with an \emph{error} level as they typically represent basic constraints; there is a reason why they have been included in the vocabulary specification. Although we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
% Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
% For some use cases, 
% validating \emph{vocabulary constraints} may be more important than validating \emph{simple} or \emph{complex constraints}.
% For other use cases,
% validating \emph{error constraints} may be sufficient without taking \emph{warning} and \emph{informational constraints} into account.
% We evaluated the (meta)data quality of large real world data sets represented by multiple and different vocabularies to get an understanding  
% (1) which sets of constraint types (on different levels of complexity) and 
% (2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).

@@

We did not detect violations of \emph{error} constraints for well-established vocabularies, even though 85\% of the QB constraints are \emph{error} constraints. 
%85\% of the QB constraints are \emph{error} constraints.
More than 50\% of the DDI-RDF and SKOS constraints are \emph{informational} constraints.
1/6 of the DDI-RDF violations are caused by \emph{error} constraints and
almost all QB and 59\% of the SKOS violations are caused by \emph{warning} constraints. 
%For well-established vocabularies, we detected no violations of \emph{error} constraints.  
%Constraints are serious when they violate the integrity of vocabularies.
%For well-established vocabularies, it is well documented and the experience is high how to guarantee this integrity
%which is not the case or newly-developed vocabularies.

\begin{hyp}
%\ke{das ist doch das gleiche wie 4, oder?}\bz{Stimme Kai zu. Finding 4 und 6 koennte man zusammenfassen oder falls es doch Unterschiede gibt, muessen die staerker hervorgehoben werden.}
For well-established vocabularies, data quality is high as serious violations rarely appear (0.3\% for QB). For newly developed vocabularies, however, data quality is worse as serious violations occur partially (1/6 for DDI-RDF).   
\end{hyp}

@@

The fact that regardless of the language 1/2 of all constraints are \emph{informational} 
%indicates that the purpose of constraints for users is mostly just to point to desirable but not necessary data improvements in terms of syntax and semantics of vocabularies. 
indicates the importance that constraint languages support
constraints on several levels. Constraints are by far not only to
prevent certain usages of a vocabulary, they are rather needed to
provide better guidance for improved interoperability.

\begin{hyp}
Regardless of the type of the used language, there are only a few violations raised by \emph{error} constraints which stands for good data quality in general.
In contrast, constraints of low severity, expressed by RDFS/OWL or high-level constraint languages, are violated to a large extent (80\%), whereas more serious constraints, expressed by SPARQL, are violated to an even larger extend (94\%).
%Violations caused by constraints expressed by RDFS/OWL or high-level constraint languages are of low severity (as the important constraints are satisfied), whereas the violation of constraints formulated by SPARQL is more serious. There is a significant demand for languages that support the expression of SPARQL Based constraints.
\end{hyp}

%The reason why there is a significant demand for languages supporting \emph{SPARQL Based} constraints is that 94\% of all violations, which are caused by \emph{SPARQL Based} constraints, are also raised by \emph{warning} constraints. This means that data quality may be improved in case these \emph{warning} constraints are adequately tackled which is more likely when these constraints are expressible not only by SPARQL but also by high-level constraint languages enabling to formulate constraints more intuitively and concisely.

94\% of the violations of SPARQL-based constraints are warnings. This
means that data quality could be improved significantly, if these
constraints are met. This is more likely when these constraints
are expressible not only by SPARQL but also by high-level
constraint languages enabling to formulate constraints more
intuitively and concisely.
